Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-12-13 main/doc/building_scope.tex
updated documentation

\section{Building Analysis Scope}
\label{sec:building-scope}

Chord computes the analysis scope (i.e., reachable classes and methods) of the given program
either if property \code{chord.build.scope} is set to \code{true} or if some other task (e.g.,
a program analysis specified via property \code{chord.run.analyses}) demands it by
calling method \code{chord.program.Program.v()}.

The algorithm used to compute the analysis scope is as follows.

\begin{itemize}
\item
If property \code{chord.reuse.scope} has value \code{true} and the files specified by properties
\code{chord.classes.file} and \code{chord.methods.file} exist,
then Chord regards those files as specifying the classes and methods, respectively,
to be regarded as reachable.  The format
of the classes file is a fully-qualified class name per line (e.g., \code{foo.bar.Main}).  The format
of the methods file is an entry of the form \code{<method name>:<method descriptor>@<class name>} per line,
specifying the method's name, the method's descriptor, and the method's declaring class
(e.g., \code{main:([Ljava/lang/String;)V@foo.bar.Main}).
Chord throws a runtime exception if the declaring class of a method in the methods file is not
specified in the classes file.

\item
If property \code{chord.reuse.scope} has value \code{false} or the file specified by
property \code{chord.classes.file} or \code{chord.methods.file} does not exist,
then Chord computes the analysis scope
using the algorithm specified by property \code{chord.scope.kind} and then
writes the classes and methods deemed reachable by that algorithm to those files.

The possible legal values of property \code{chord.scope.kind} are \code{rta} and \code{dynamic}.
In both cases, Chord expects properties \code{chord.main.class} and \code{chord.class.path}
to be set.

\begin{itemize}
\item
The \code{rta} value instructs Chord to compute the analysis scope statically using Rapid Type Analysis.

\item
The \code{dynamic} value instructs Chord to compute the analysis scope dynamically, by running the program
and observing using JVMTI the classes that are loaded at run-time.
The number of times the program is run and the command-line arguments to be supplied to
the program in each run is specified by properties \code{chord.run.ids} and
\code{chord.args.<id>} for each run ID \code{<id>}.  By default, the program is run only once, using run ID \code{0},
and without any command-line arguments.
Only classes loaded in some run are regarded as reachable but {\it all} methods of each loaded class are regarded
as reachable regardless of whether they were invoked in the run.
The rationale behind this decision is to both reduce run-time overhead of JVMTI and to increase the
predictive power of program analyses performed using the computed analysis scope.
\end{itemize}
\end{itemize}

The default value of property \code{chord.reuse.scope} is \code{false} and that of
property \code{chord.scope.kind} is \code{rta}.
The default values of properties \code{chord.classes.file} and \code{chord.methods.file} are
\code{[chord.out.dir]/classes.txt} and \code{[chord.out.dir]/methods.txt}, respectively,
where property \code{chord.out.dir} defaults to \code{[chord.work.dir]/chord_output/},
and property \code{chord.work.dir} defaults to the current working directory.

>>>>

\section{Computing Program Scope}
\label{sec:building-scope}

\Chord\ computes the scope (i.e., reachable methods) of the given
program either if property \code{chord.build.scope} is set to {\tt
  true} or if some other task (e.g., a program analysis specified via
property \code{chord.run.analyses}) demands it by calling method
\code{chord.program.Program.g()}.

Users can set the following properties to control scope computation:

\begin{itemize}
\item \code{chord.main.class}
\item \code{chord.class.path}
\item \code{chord.reuse.scope}
\item \code{chord.methods.file}
\item \code{chord.reflect.file}
\item \code{chord.scope.kind}
\item \code{chord.ch.kind}
\item \code{chord.reflect.kind}
\item \code{chord.std.scope.exclude}
\item \code{chord.ext.scope.exclude}
\item \code{chord.scope.exclude}
\end{itemize}

\subsection{Reusing Program Scope}

If property \code{chord.reuse.scope} has value {\tt true} and both
files specified by properties \code{chord.methods.file} and
\code{chord.reflect.file} exist, then \Chord\ regards those files as
specifying which methods to consider reachable and how to resolve
reflection, respectively.

The format of the file specified by property \code{chord.methods.file}
is a list of zero or more lines, where each line is of the form
\code{mname:mdesc@cname}
specifying the method's name {\tt mname}, the method's descriptor
{\tt mdesc}, and the method's declaring class {\tt cname} (e.g.,
\code{main:([Ljava/lang/String;)V@foo.bar.Main}).

The format of the file specified by property \code{chord.reflect.file}
is of the form:
\begin{verbatim}
# resolvedClsForNameSites
...
# resolvedObjNewInstSites
...
# resolvedConNewInstSites
...
# resolvedAryNewInstSites
...
\end{verbatim}
where each of the above ``{\tt ...}'' is a list of zero or more lines, where
each line is of the form
\code{bci!mname:mdesc@cname->type1,type2,...typeN}
meaning the call site at bytecode offset {\tt bci} in the
method denoted by {\tt mname:mdesc@cname} may resolve to any of
reference types {\tt type1}, {\tt type2}, ..., {\tt typeN}.
The meaning of the above four sections is as follows.
\begin{itemize}
\item {\tt resolvedClsForNameSites} lists
each call to static method {\tt forName(String)} defined in class
{\tt java.lang.Class}, along with a list of the types of the named
classes.
\item {\tt resolvedObjNewInstSites} lists
each call to instance method {\tt newInstance()} defined in class
{\tt java.lang.Class}, along with a list of the types of the
instantiated classes.
\item {\tt resolvedConNewInstSites} lists
each call to instance method {\tt newInstance(Object[])} defined in class
{\tt java.lang.reflect.Constructor}, along with a list of the types of the
instantiated classes.
\item {\tt resolvedAryNewInstSites} lists
each call to instance method {\tt newInstance(Class,int)} defined in class
{\tt java.lang.reflect.Array}, along with a list of the types of the
instantiated classes.
\end{itemize}
The default value of property \code{chord.reuse.scope} is {\tt false}.
The default value of properties \code{chord.methods.file} and
\code{chord.reflect.file} is \code{[chord.out.dir]/methods.txt} and
\code{[chord.out.dir]/reflect.txt}, respectively.
Property \code{chord.out.dir} defaults to
\code{[chord.work.dir]/chord_output/} and property
\code{chord.work.dir} defaults to the working directory during Chord's
execution.

\subsection{Scope Construction Algorithms}

If property \code{chord.reuse.scope} has value {\tt false} or the
files specified by properties \code{chord.methods.file} or
\code{chord.reflect.file} do not exist, then \Chord\ computes program
scope using the algorithm specified by property
\code{chord.scope.kind} and then writes the list of methods deemed
reachable and the reflection resolved by that algorithm to the files
specified by properties \code{chord.methods.file} and
\code{chord.reflect.file}, respectively.

The possible legal values of property \code{chord.scope.kind} are
[\code{dynamic}$|$\code{rta}$|$\code{cha}].  In each case, \Chord\ at
least expects properties \code{chord.main.class} and
\code{chord.class.path} to be set.

\begin{itemize}
\item
The {\tt dynamic} value instructs \Chord\ to compute program scope
dynamically, by running the program and observing using JVMTI the
classes that are loaded at run-time.  The number of times the program
is run and the command-line arguments to be supplied to the program in
each run is specified by properties \code{chord.run.ids} and
\code{chord.args.<id>} for each run ID {\tt <id>}.  By default, the
program is run only once, using run ID {\tt 0}, and without any
command-line arguments.  Only classes loaded in some run are regarded
as reachable but {\it all} methods of each loaded class are regarded
as reachable regardless of whether they were invoked in the run.  The
rationale behind this decision is to both reduce run-time overhead of
JVMTI and to increase the predictive power of program analyses
performed using the computed program scope.

\item
The {\tt rta} value instructs \Chord\ to compute program scope
statically using Rapid Type Analysis (RTA).

RTA is an iterative fixed-point algorithm.  It maintains a set of
reachable methods $M$.  The initial iteration starts by assuming that
only the main method in the main class is reachable (\Chord\ also
handles class initializer methods but we ignore them here for brevity;
we also ignore the set of reachable classes maintained besides the set
of reachable methods).  All object allocation sites $H$ contained in
methods in $M$ are deemed reachable (i.e., control-flow within method
bodies is ignored).  Whenever a dynamically-dispatching method call
site (i.e., an invokevirtual or invokeinterface site) with receiver of
static type $t$ is encountered in a method in $M$, only subtypes of
$t$ whose objects are allocated at some site in $H$ are considered to
determine the possible target methods, and each such target method is
added to $M$.  The process terminates when no more methods can be
added.

%RTA is a relatively inexpensive and precise algorithm in practice.  Its key shortcoming is that it makes
%no attempt to resolve reflection, which is rampant in real-world Java programs, and can therefore be
%unsound (i.e., underestimate the set of reachable classes and methods).
%The next option attempts to overcome this problem.
%
%\item
%The \code{rta_reflect} value instructs \Chord\ to compute program scope statically using Rapid Type Analysis
%and, moreover, to resolve a common reflection pattern:
%
%\begin{quote}
%\begin{verbatim}
%String s = ...;
%Class c = Class.forName(s);
%Object o = c.newInstance();
%T t = (T) o;
%\end{verbatim}
%\end{quote}
%
%This analysis is identical to RTA except that it additionally inspects every cast statement in the program,
%such as the last statement in the above snippet,
%and queries the class hierarchy to find all concrete classes that subclass \code{T} (if \code{T} is a class)
%or that implement \code{T} (if \code{T} is an interface).
%\Chord\ allows users to control which classes are included in the class hierarchy (see below).
%
\item
The {\tt cha} value instructs \Chord\ to compute program scope
statically using Class Hierarchy Analysis (CHA).

The key difference between CHA and RTA is that for invokevirtual and
invokeinterface sites with receiver of static type $t$, CHA considers
{\it all} subtypes of $t$ in the class hierarchy to determine the
possible target methods, whereas RTA restricts them to types of
objects allocated in methods deemed reachable so far.  As a result,
CHA is highly imprecise in practice, and also expensive since it
grossly overestimates the set of reachable classes and methods.
Nevertheless, \Chord\ allows users to control which classes are
included in the class hierarchy (see below) and thereby control the
precision and cost of CHA.

\end{itemize}
The default value of property \code{chord.scope.kind} is {\tt rta}.

\subsection{Class Hierarchy Construction}

The class hierarchy is built if property \code{chord.scope.kind} has
value {\tt cha}.  Users can control which classes are included in
building the class hierarchy by setting property \code{chord.ch.kind},
whose possible legal values are [\code{static}$|$\code{dynamic}].
\Chord\ first constructs the entire classpath of the given program by
concatenating in order the following classpaths:

\begin{enumerate}
\item
The boot classpath, specified by property \code{sun.boot.class.path}.
\item
The library extensions classpath, comprising all jar files in
directory \code{[java.home]/lib/dir/}.
\item
\Chord's classpath, specified by property
\code{chord.main.class.path}.  This includes the classpath of any
user-defined Java analyses, specified by user-defined property
\code{chord.java.analysis.path}, which is empty by default.
\item
The classpath of the given program, specified by user-defined property
\code{chord.class.path}, which is empty by default.
\end{enumerate}

All classes in the entire classpath (resulting from items 1--4 above)
are included in the class hierarchy with the following exceptions:
\begin{itemize}
\item
Duplicate classes, i.e., classes with the same name occurring in more
than one classpath element; in this case, all occurrences except the
first are excluded.
\item
Any class whose name's prefix is specified in the value of property
\code{chord.scope.exclude}.
\item
If property \code{chord.ch.kind} has value {\tt dynamic}, then
\Chord\ runs the given program and observes the set of all classes the
JVM loads; any class not in this set is excluded.  By default,
property \code{chord.ch.kind} has value {\tt static}.
\item
If the superclass of a class C is missing or if an interface
implemented/extended by a class/interface C is missing, where
``missing" means that it is either not in the classpath resulting from
items 1--4 above or it is excluded by one of these rules, then C
itself is excluded.  Note that this rule is recursive, e.g., if C has
superclass B which in turn has superclass A, and A is missing, then
both B and C are excluded.
\end{itemize}

\subsection{Scope Exclusion}

%TODO: describe chord.scope.exclude?

%\begin{tabular}
%chord.scope.kind,chord.ch.dynamic & runs program? & \# reachable classes & \# reachable methods & running time \\
%dynamic,-         & yes &    314 &  4,491 &   25s \\
%cha,true          & yes &    427 &  1,532 &   28s \\
%rta,-             &  no &    849 &  4,836 &    9s \\
%rta_reflect,true  & yes &    849 &  4,836 &   34s \\
%rta_reflect,false &  no &  9,871 & 58,726 &  7m6s \\
%cha,false         &  no & 14,121 & 74,613 & 4m11s
%\end{tabular}

### 2010-12-13 main/doc/chord_sysprops.tex
updated documentation

\begin{itemize}
\item
\code{chord.build.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute the scope (i.e., reachable classes and methods) of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}.

@@

This section describes properties that specify how the analysis scope is computed.
See Section \ref{sec:building-scope} for more details.

\begin{itemize}
\item
\code{chord.reuse.scope} \\
{\bf Type:} bool \\
{\bf Description:} Treat analysis scope as the classes and methods listed in files specified by properties \code{chord.classes.file} and \code{chord.methods.file}, respectively.  Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. \\
{\bf Default value:} {\tt false}

\item
\code{chord.scope.kind} \\
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute analysis scope (i.e., reachable classes and methods).  Current choices include {\tt dynamic} (dynamic analysis), {\tt rta} (static Rapid Type Analysis), and {\tt cha} (static Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

@@

\item
\code{chord.scope.exclude.std} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes inside the standard library whose method bodies must be treated as no-ops by static scope building algorithms. \\
{\bf Default value:} \code{[chord.main.class.path]}

\item
\code{chord.scope.exclude.ext} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes outside the standard library whose method bodies must be treated as no-ops by static scope building algorithms. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes whose method bodies must be treated as no-ops by static scope building algorithms. \\
{\bf Default value:} \code{"[chord.main.class.path],[chord.scope.exclude.ext]"}
\end{itemize}

@@

\item
\code{chord.dlog.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.main.dir]/src/dlog/:[chord.main.dir]/../extra/src/dlog/}

@@

\code{chord.check.exclude.std} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"sun.,com.sun.,com.ibm.jvm.,com.ibm.oti.,com.ibm.misc.,org.apache.harmony.,joeq.,jwutil.,java.,javax."}

\item
\code{chord.check.exclude.ext} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages outside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.check.exclude.std],[chord.check.exclude.ext]"}
\end{itemize}

@@

\begin{itemize}
\item
\code{chord.ssa} \\
{\bf Type:} bool \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute analysis scope. \\
{\bf Default value:} {\tt true} 
\end{itemize}

>>>>

\begin{itemize}
\item
\code{chord.build.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute the scope of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}.

@@

This section describes properties that specify how the program scope is computed.
See Section \ref{sec:building-scope} for more details.

\begin{itemize}
\item
\code{chord.reuse.scope} \\
{\bf Type:} bool \\
{\bf Description:} Compute program scope using the information in files specified by properties \code{chord.methods.file} and \code{chord.reflect.file}.  Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. \\
{\bf Default value:} {\tt false}

\item
\code{chord.scope.kind} \\
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  Current choices include {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

@@

\item
\code{chord.std.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes inside the standard library whose method bodies must be treated as no-ops. \\
{\bf Default value:} \code{[chord.main.class.path]}

\item
\code{chord.ext.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes outside the standard library whose method bodies must be treated as no-ops. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.scope.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes whose method bodies must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{itemize}

@@

\item
\code{chord.dlog.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.main.dir]/src/}

@@

\code{chord.std.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"sun.,com.sun.,com.ibm.jvm.,com.ibm.oti.,com.ibm.misc.,org.apache.harmony.,joeq.,jwutil.,java.,javax."}

\item
\code{chord.ext.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages outside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}

\item
\code{chord.check.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.std.check.exclude],[chord.ext.check.exclude]"}
\end{itemize}

@@

\begin{itemize}
\item
\code{chord.ssa} \\
{\bf Type:} bool \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute program scope. \\
{\bf Default value:} {\tt true} 
\end{itemize}

### 2010-12-13 main/doc/program_setup.tex
updated documentation

\begin{quote}
\begin{verbatim}
example/
    src/
        foo/
            Main.java
            ...
    classes/
        foo/
            Main.class
            ...
    lib/
        src/
            taz/
                ...
        jar/
            taz.jar
    chord.properties
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
chord.main.class=foo.Main
chord.class.path=classes:lib/jar/taz.jar
chord.src.path=src:../lib/src
chord.run.ids=0,1
chord.args.0="-thread 1 -n 10"
chord.args.1="-thread 2 -n 50"
\end{verbatim}
\end{quote}

@@

\begin{quote}
\begin{verbatim}
prompt> ant -Dchord.work.dir=<...>/example run
\end{verbatim}
\end{quote}

\noindent where {\tt <...>} denotes either the absolute path, or the path relative to Chord's {\tt main/} directory,
of the parent of directory {\tt example/}.
System property \code{chord.work.dir} specifies the working directory during Chord's execution.

>>>>

\begin{verbatim}
    example/
        src/
            foo/
                Main.java
                ...
        classes/
            foo/
                Main.class
                ...
        lib/
            src/
                taz/
                    ...
            jar/
                taz.jar
        chord.properties
\end{verbatim}

@@

\begin{verbatim}
    chord.main.class=foo.Main
    chord.class.path=classes:lib/jar/taz.jar
    chord.src.path=src:../lib/src
    chord.run.ids=0,1
    chord.args.0="-thread 1 -n 10"
    chord.args.1="-thread 2 -n 50"
\end{verbatim}

@@

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<...>/example run
\end{verbatim}

\noindent where {\tt <...>} denotes the absolute path of the parent of
directory {\tt example/}.  Property \code{chord.work.dir} specifies
the working directory during Chord's execution.

### 2010-12-13 main/doc/whatis_chord.tex
updated documentation

\Chord\ is a static and dynamic program analysis framework for Java.
It has the following key characteristics:

\begin{itemize}
\item
Stand-alone: various off-the-shelf program analyses are provided (e.g., may-alias, thread-escape, datarace, deadlock, etc.).
\item
Extensible: users can build their own program analyses on top of the provided ones.
\item
Compositional: each program analysis can be written independently and yet made to interact in complex ways with other program analyses.
\item
Efficient: results computed by each program analysis are cached for reuse by other program analyses without re-computation.
\item
Flexible: a broad range of program analyses can be expressed, including those
written imperatively in Java or declaratively in Datalog, summary-based as well as cloning-based context-sensitive analyses,
iterative refinement-based analyses, client-driven analyses, and combined static and dynamic analyses.
\end{itemize}

\noindent \Chord\ is intended for use by a broad range of users:

\begin{itemize}
\item
Program analysis writers: Program analysis researchers wanting to implement and evaluate new program analysis algorithms.
\item
Program analysis appliers: Researchers with possibly a limited program analysis background wanting to build applications on
top of program analyses in Chord used as black boxes.
\item
Software engineers: Programmers wanting to use program analyses in Chord to assist with software development and testing.
\end{itemize}

\noindent \Chord\ is intended to work on a variety of platforms, including Linux, Windows/Cygwin, and MacOS.
It has been tested most extensively on Linux.
It is open source software distributed under the \htmladdnormallink{New BSD License}{http://www.opensource.org/licenses/bsd-license.php}.
Contributions from users are welcome and encouraged.
The project website is located at \url{http://code.google.com/p/jchord/}.

>>>>

\Chord\ is a program analysis platform for Java designed with the
primary goal of helping advance the state-of-the-art in the field by
enabling researchers to productively design, implement, and evaluate a
broad variety of program analyses. To this end, Chord has the
following key characteristics:

\begin{itemize}
\item
Stand-alone: it provides various off-the-shelf analyses (e.g., various
call-graph analyses; points-to analyses; thread-escape analysis;
static slicing; static and dynamic concurrency analyses for finding
races, deadlocks, and atomicity violations; etc.)
\item
Extensible: it allows users to build their own analyses atop the
provided analyses.
\item
Compositional: it allows users to write each analysis independently
yet allow it to interact in complex ways with other analyses by
specifying lightweight data- and control-dependencies.
\item
Efficient: It executes analyses in a demand-driven fashion, caches
results computed by each analysis for reuse by other analyses without
re-computation, and can execute analyses without dependencies between
them in parallel.
\item
Deterministic: It guarantees that the result is the same regardless of
the order in which different analyses are executed; moreover, results
can be shared across different runs.
\item
Flexible: It allows a broad range of analyses to be expressed,
including both static and dynamic analyses, analyses written
imperatively in Java or declaratively in Datalog, summary-based as
well as cloning-based inter-procedural context-sensitive analyses,
iterative refinement-based analyses, client-driven analyses, and
combined static/dynamic analyses.
\end{itemize}

\noindent \Chord\ is intended to work on a variety of platforms,
including Linux, Windows/Cygwin, and MacOS.  It has been tested most
extensively on Linux.  It is open source software distributed under
the \htmladdnormallink{New BSD
  License}{http://www.opensource.org/licenses/bsd-license.php}.
Improvements by users are welcome and encouraged.  The project website
is \url{http://berkeley.intel-research.net/chord/} and the software
website is \url{http://code.google.com/p/jchord/}.
